---
title: "Baby_names_script"
author: "Olaf König"
format:
  html:
    self-contained: true
    page-layout: full
    toc: true
    toc-depth: 4
    number-sections: true
    number-depth: 4
    code-line-numbers: true
    code-fold: true
execute:
  warning: false
  message: false
theme: cosmo
editor: visual
---

# Swiss First Names Analysis - Automated Annual Report

## Objectives

**Main goal:** Automated analysis of Swiss baby names with historical trends and multilingual article generation.

**Goals:**

-   Get newborn data from PX Web cubes (automatic download with new year) - Get living population data from CSV files (manual URLs - update annually)

-   Generate comprehensive analysis with rankings, trends, and changes - Produce automated multilingual articles (FR/DE/EN) ready for publication - Create interactive visualizations and summary exports

**Usage:**

**Note:** Living population CSV URLs must be updated manually each year using browser inspector to find direct download links.

------------------------------------------------------------------------

## Inputs

| Object Name | File Name | Source | Extension |
|---------------------|-----------------|-----------------|-----------------|
| babynames_female | px_names_female_YYYY | <https://www.pxweb.bfs.admin.ch/pxweb/fr/px-x-0104050000_102/-/px-x-0104050000_102.px/table/tableViewLayout2/> | .csv |
| babynames_male | px_names_male_YYYY | <https://www.pxweb.bfs.admin.ch/pxweb/fr/px-x-0104050000_101/-/px-x-0104050000_101.px/table/tableViewLayout2/> | .csv |
| all_female_names_ch **2023** | all_female_names_ch_2023 | <https://www.bfs.admin.ch/bfs/fr/home/statistiques/population/naissances-deces/noms-suisse.assetdetail.32208758.html> | .csv |
| all_female_names_ch **2024** | all_female_names_ch_2024 | <https://www.bfs.admin.ch/bfs/fr/home/statistiques/population/naissances-deces/noms-suisse.assetdetail.36062347.html> | .csv |
| all_male_names_ch **2023** | all_male_names_ch_2023 | <https://www.bfs.admin.ch/bfs/fr/home/statistiques/population/naissances-deces/noms-suisse.assetdetail.32208755.html> | .csv |
| all_male_names_ch **2024** | all_male_names_ch_2024 | <https://www.bfs.admin.ch/bfs/fr/home/statistiques/population/naissances-deces/noms-suisse.assetdetail.36062345.html> | .csv |

## Outputs

| Object Name | File Name | Description | Extension |
|-------------------|-----------------|-------------------|-----------------|
| results_summary | name_analysis_summary_YYYY | Key metrics and rankings summary | .csv |
| article_fr | article_fr_YYYY | French article with automated text | .html |
| article_de | article_de_YYYY | German article with automated text | .html |
| article_en | article_en_YYYY | English article with automated text | .html |
| top3_evolution_male | \- | Interactive heatmap - male names evolution | plotly |
| top3_evolution_female | \- | Interactive heatmap - female names evolution | plotly |
| length_evolution_chart | \- | Interactive chart - name length trends | plotly |
| rankings_tables | \- | Interactive tables - rankings by region/gender | DT |

------------------------------------------------------------------------

# Generic setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = TRUE,
  message = TRUE,
  fig.width = 10,
  fig.height = 6
)
```

```{r libraries, message=FALSE}
library(tidyverse)
library(tidylog)
library(here)
library(janitor)
library(lubridate)
library(DT)
library(plotly)
library(viridis)
library(glue)
library(scales)


# Custom theme for plots
theme_set(theme_minimal())

# Disable scientific notation
options(scipen = 999)
# # Re-enable scientific notation (default behavior)
# options(scipen = 0)
```

```{r setup-paths}
# Define project paths
input_raw_dir <- here("input", "raw")
input_processed_dir <- here("input", "processed") 
output_dir <- here("output")
```

------------------------------------------------------------------------

# Data Import

# Swiss First Names Analysis

## Configuration

```{r config}
# =============================================================================
# CONFIGURATION - UPDATE ANNUALLY
# =============================================================================

# Reference year (published data is always current year - 1)
current_year <- year(Sys.Date())
data_year <- current_year - 1
comparison_year <- data_year - 1

cat("Current year:", current_year, "\n")
cat("Data year:", data_year, "\n") 
cat("Comparison year:", comparison_year, "\n")

# URLs to update manually each year
urls_config <- list(
  # PX Web (automatic - complete historical data)
  px_female = "https://www.pxweb.bfs.admin.ch/sq/ea826a26-7e80-4906-a4f2-d89a145cd19e",
  px_male = "https://www.pxweb.bfs.admin.ch/sq/7a95b4e9-f6d8-49cc-858d-cea658ac3a2b",
  
  # All names - current year (manual - population snapshot)
  all_female_current = "https://dam-api.bfs.admin.ch/hub/api/dam/assets/36062347/master",
  all_male_current = "https://dam-api.bfs.admin.ch/hub/api/dam/assets/36062345/master",
  
  # All names - previous year (for stock evolution comparison)
  all_female_previous = "https://dam-api.bfs.admin.ch/hub/api/dam/assets/32208758/master",
  all_male_previous = "https://dam-api.bfs.admin.ch/hub/api/dam/assets/32208755/master"
)
```

## Import Functions

```{r functions}
# =============================================================================
# IMPORT FUNCTIONS
# =============================================================================

# Function for PX Web data (with UTF-8 conversion)
import_px_data <- function(url, filename_base, year) {
  filename <- paste0(filename_base, "_", year, ".csv")
  file_path <- file.path(input_raw_dir, filename)
  
  # Create directory if needed
  dir.create(dirname(file_path), showWarnings = FALSE, recursive = TRUE)
  
  # Download
  download.file(url, destfile = file_path, mode = "wb")
  
  # UTF-8 conversion
  lines <- readLines(file_path, encoding = "Windows-1252")
  lines_utf8 <- iconv(lines, from = "Windows-1252", to = "UTF-8")
  writeLines(lines_utf8, file(file_path, encoding = "UTF-8"))
  
  # Read data
  data <- readr::read_csv(file_path) %>%
    janitor::clean_names()
  
  message("✅ ", filename, " imported successfully")
  return(data)
}

# Function for direct CSV downloads
import_csv_data <- function(url, filename_base, year, gender) {
  filename <- paste0(filename_base, "_", year, ".csv")
  file_path <- file.path(input_raw_dir, filename)
  
  # Download
  download.file(url, file_path, mode = "wb")
  
  # Read data
  data <- read_csv(file_path, locale = locale(encoding = "UTF-8")) %>%
    janitor::clean_names() %>%
    mutate(gender = gender) %>%
    select(-obs_status)
  
  message("✅ ", filename, " imported successfully")
  return(data)
}
```

## Data Import

```{r import}
# =============================================================================
# DATA IMPORT
# =============================================================================

# PX Data (newborns by region and year)
assign(paste0("px_names_female_", data_year), 
       import_px_data(urls_config$px_female, "px_names_female", data_year))

assign(paste0("px_names_male_", data_year), 
       import_px_data(urls_config$px_male, "px_names_male", data_year))

# All names - current year snapshot
assign(paste0("all_female_names_ch_", data_year),
       import_csv_data(urls_config$all_female_current, "all_female_names_ch", data_year, "female"))

assign(paste0("all_male_names_ch_", data_year),
       import_csv_data(urls_config$all_male_current, "all_male_names_ch", data_year, "male"))

# All names - previous year snapshot (for comparisons)
assign(paste0("all_female_names_ch_", comparison_year),
       import_csv_data(urls_config$all_female_previous, "all_female_names_ch", comparison_year, "female"))

assign(paste0("all_male_names_ch_", comparison_year),
       import_csv_data(urls_config$all_male_previous, "all_male_names_ch", comparison_year, "male"))

# Control output
cat("📊 Data imported for year:", data_year, "\n")
cat("🔍 Comparison year:", comparison_year, "\n")
cat("📁 Files saved in:", input_raw_dir, "\n")
```

## Data Quality Check

```{r check-functions}
# =============================================================================
# ENCODING CHECK FUNCTION
# =============================================================================

# Function to check encoding issues in name columns
check_encoding <- function(df, col) {
  col <- enquo(col)  # capture the column
  
  df %>%
    mutate(.value = as.character(!!col)) %>%
    # Find characters that are NEITHER letters NOR hyphens
    filter(str_detect(.value, "[^[:alpha:]-]")) %>%
    distinct(.value) %>% 
    arrange(.value)
}
```

```{r encoding-checks}
# =============================================================================
# ENCODING VERIFICATION
# =============================================================================

# Get current datasets (using get() to access dynamically named objects)
px_female_current <- get(paste0("px_names_female_", data_year))
px_male_current <- get(paste0("px_names_male_", data_year))
all_female_current <- get(paste0("all_female_names_ch_", data_year))
all_male_current <- get(paste0("all_male_names_ch_", data_year))

# Check encoding issues
cat("🔍 Checking encoding issues...\n")

cat("\nPX Female names with encoding issues:\n")
print(check_encoding(px_female_current, prenom))

cat("\nPX Male names with encoding issues:\n")
print(check_encoding(px_male_current, prenom))

cat("\nAll female names with encoding issues:\n")
print(check_encoding(all_female_current, firstname))

cat("\nAll male names with encoding issues:\n")
print(check_encoding(all_male_current, firstname))

cat("✅ Encoding checks completed\n")
```

## ------------------------------------------------------------------------

# Chapter 1 - Rankings and Podiums

```{r setup-ch1, include=FALSE}
library(tidyverse)
library(DT)

# Configuration parameters
top_n_analysis <- 200
top_n_display <- 100
```

## Data Processing

```{r data-processing}
# Get current datasets
px_female_current <- get(paste0("px_names_female_", data_year))
px_male_current <- get(paste0("px_names_male_", data_year))

# Transform PX data from wide to long format
px_female_long <- px_female_current %>%
  pivot_longer(cols = starts_with("x"), 
               names_to = "year", 
               values_to = "value") %>%
  mutate(
    year = as.numeric(str_remove(year, "x")),
    gender = "female"
  ) %>%
  filter(!is.na(value))

px_male_long <- px_male_current %>%
  pivot_longer(cols = starts_with("x"), 
               names_to = "year", 
               values_to = "value") %>%
  mutate(
    year = as.numeric(str_remove(year, "x")),
    gender = "male"
  ) %>%
  filter(!is.na(value))

# Combine both datasets
px_names_combined <- bind_rows(px_female_long, px_male_long)

# Create custom rankings (unique ranks: by count DESC then alphabetically)
px_names_with_custom_ranks <- px_names_combined %>%
  filter(unite_de_mesure == "Nombre") %>%  # Use counts only
  group_by(region_linguistique_canton, year, gender) %>%
  arrange(desc(value), prenom) %>%
  mutate(custom_rank = row_number()) %>%
  ungroup()

cat("✅ Data transformation completed\n")
cat("Years available:", min(px_names_with_custom_ranks$year), "-", max(px_names_with_custom_ranks$year), "\n")
```

## 1.1 National Top 3 Rankings

### Top 3 Male Names {data_year}

```{r national-top3-male}
# Extract national top 3 male names for current year
national_top3_male <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         year == data_year,
         gender == "male",
         custom_rank <= 3) %>%
  select(prenom, value, custom_rank) %>%
  arrange(custom_rank)

# Print results
print("National Top 3 Male Names:")
print(national_top3_male)

# Display as datatable
datatable(national_top3_male, 
          colnames = c("First Name", "Count", "Rank"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Top 3 Male Names in Switzerland", data_year))
```

### Top 3 Female Names {data_year}

```{r national-top3-female}
# Extract national top 3 female names for current year
national_top3_female <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         year == data_year,
         gender == "female",
         custom_rank <= 3) %>%
  select(prenom, value, custom_rank) %>%
  arrange(custom_rank)

# Print results
print("National Top 3 Female Names:")
print(national_top3_female)

# Display as datatable
datatable(national_top3_female, 
          colnames = c("First Name", "Count", "Rank"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Top 3 Female Names in Switzerland", data_year))
```

## 1.2 Regional Top 3 Rankings

### Top 3 Male Names by Linguistic Region

```{r regional-top3-male}
# Extract regional top 3 male names
regional_top3_male <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton %in% c("Suisse alémanique", "Suisse romande", "Suisse italienne"),
         year == data_year,
         gender == "male",
         custom_rank <= 3) %>%
  select(region_linguistique_canton, prenom, value, custom_rank) %>%
  arrange(region_linguistique_canton, custom_rank)

# Print results
print("Regional Top 3 Male Names:")
print(regional_top3_male)

# Display as datatable
datatable(regional_top3_male, 
          colnames = c("Region", "First Name", "Count", "Rank"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Top 3 Male Names by Linguistic Region", data_year))
```

### Top 3 Female Names by Linguistic Region

```{r regional-top3-female}
# Extract regional top 3 female names
regional_top3_female <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton %in% c("Suisse alémanique", "Suisse romande", "Suisse italienne"),
         year == data_year,
         gender == "female",
         custom_rank <= 3) %>%
  select(region_linguistique_canton, prenom, value, custom_rank) %>%
  arrange(region_linguistique_canton, custom_rank)

# Print results
print("Regional Top 3 Female Names:")
print(regional_top3_female)

# Display as datatable
datatable(regional_top3_female, 
          colnames = c("Region", "First Name", "Count", "Rank"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Top 3 Female Names by Linguistic Region", data_year))
```

## Store Results for Text Generation

```{r store-results-ch1}
# Initialize results structure
if (!exists("results")) {
  results <- list()
}

# Store national rankings
results$rankings <- list(
  national = list(
    male = national_top3_male$prenom,
    female = national_top3_female$prenom
  ),
  regional = list(
    alemanique = list(
      male = regional_top3_male %>% filter(region_linguistique_canton == "Suisse alémanique") %>% pull(prenom),
      female = regional_top3_female %>% filter(region_linguistique_canton == "Suisse alémanique") %>% pull(prenom)
    ),
    romande = list(
      male = regional_top3_male %>% filter(region_linguistique_canton == "Suisse romande") %>% pull(prenom),
      female = regional_top3_female %>% filter(region_linguistique_canton == "Suisse romande") %>% pull(prenom)
    ),
    italienne = list(
      male = regional_top3_male %>% filter(region_linguistique_canton == "Suisse italienne") %>% pull(prenom),
      female = regional_top3_female %>% filter(region_linguistique_canton == "Suisse italienne") %>% pull(prenom)
    )
  )
)

cat("✅ Chapter 1 results stored\n")
```

## ------------------------------------------------------------------------

# Chapter 2 - Evolution and Stability of Leaders

```{r setup-ch2, include=FALSE}
library(tidyverse)
library(DT)
library(plotly)
library(viridis)
```

## 2.1 Years as #1 Leader

### Male Leader Analysis

```{r male-leader-years}
# Find current #1 male name
current_male_leader <- results$rankings$national$male[1]

# Find all years where this name was #1 nationally
male_leader_years <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "male",
         custom_rank == 1) %>%
  filter(prenom == current_male_leader) %>%
  select(year, prenom, value) %>%
  arrange(year)

# Summary
male_leader_summary <- tibble(
  name = current_male_leader,
  total_years_as_leader = nrow(male_leader_years),
  years_list = list(male_leader_years$year)
)

# Print results
print(paste("Male leader analysis for:", current_male_leader))
print(male_leader_summary)
print("Years as #1:")
print(male_leader_years)

# Display as datatable
datatable(male_leader_years, 
          colnames = c("Year", "Name", "Count"),
          options = list(dom = 't', pageLength = 20),
          caption = paste("Years when", current_male_leader, "was #1 nationally"))
```

### Female Leader Analysis

```{r female-leader-years}
# Find current #1 female name
current_female_leader <- results$rankings$national$female[1]

# Find all years where this name was #1 nationally
female_leader_years <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "female",
         custom_rank == 1) %>%
  filter(prenom == current_female_leader) %>%
  select(year, prenom, value) %>%
  arrange(year)

# Summary
female_leader_summary <- tibble(
  name = current_female_leader,
  total_years_as_leader = nrow(female_leader_years),
  years_list = list(female_leader_years$year)
)

# Print results
print(paste("Female leader analysis for:", current_female_leader))
print(female_leader_summary)
print("Years as #1:")
print(female_leader_years)

# Display as datatable
datatable(female_leader_years, 
          colnames = c("Year", "Name", "Count"),
          options = list(dom = 't', pageLength = 20),
          caption = paste("Years when", current_female_leader, "was #1 nationally"))
```

## 2.2 Top 3 Evolution Over Time

### Male Top 20 Evolution (Last 10 Years)

```{r male-top20-evolution}
# Get current year top 20 male names (ordered by current rank)
male_current_top20 <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "male",
         year == data_year,
         custom_rank <= 20) %>%
  arrange(custom_rank) %>%
  pull(prenom)

# Get evolution for last 10 years
years_range <- seq(data_year - 9, data_year)

male_evolution_matrix <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "male",
         year %in% years_range,
         prenom %in% male_current_top20) %>%
  select(year, prenom, custom_rank) %>%
  complete(year, prenom, fill = list(custom_rank = NA)) %>%
  # Order names by current year ranking
  mutate(prenom = factor(prenom, levels = male_current_top20))

# Print evolution data
print("Male Top 20 Evolution (Last 10 Years):")
print(male_evolution_matrix %>% arrange(prenom, year))

# Create improved heatmap with exact color mapping
max_rank <- 20
# 3 fixed colors for ranks 1/2/3 then blue gradient for 4..20
blue_ramp <- colorRampPalette(c("#deebf7", "#9ecae1", "#3182bd"))(max_rank - 3)
rank_colors <- c("#e34a33", "#fdbb84", "#fee8c8", blue_ramp)
names(rank_colors) <- 1:max_rank

male_heatmap_improved <- male_evolution_matrix %>%
  ggplot(aes(x = year, y = prenom, fill = factor(custom_rank))) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = ifelse(is.na(custom_rank), "", custom_rank)), 
            color = "black", fontface = "bold", size = 3) +
  # Manual color scale with exact mapping
  scale_fill_manual(
    values = rank_colors,
    na.value = "grey90",
    name = "Rank"
  ) +
  scale_y_discrete(limits = rev(levels(male_evolution_matrix$prenom))) +
  labs(title = "Male Names Evolution - Last 10 Years (Current Top 20)",
       x = "Year", y = "Name") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank())

# Convert to plotly
male_heatmap_plotly <- ggplotly(male_heatmap_improved, 
                                tooltip = c("x", "y", "fill")) %>%
  layout(hovermode = "closest")

male_heatmap_plotly
```

### Female Top 20 Evolution (Last 10 Years)

```{r female-top20-evolution}
# Get current year top 20 female names (ordered by current rank)
female_current_top20 <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "female",
         year == data_year,
         custom_rank <= 20) %>%
  arrange(custom_rank) %>%
  pull(prenom)

# Get evolution for last 10 years
female_evolution_matrix <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         gender == "female",
         year %in% years_range,
         prenom %in% female_current_top20) %>%
  select(year, prenom, custom_rank) %>%
  complete(year, prenom, fill = list(custom_rank = NA)) %>%
  # Order names by current year ranking
  mutate(prenom = factor(prenom, levels = female_current_top20))

# Print evolution data
print("Female Top 20 Evolution (Last 10 Years):")
print(female_evolution_matrix %>% arrange(prenom, year))

# Create improved heatmap with exact color mapping
max_rank <- 20
# 3 fixed colors for ranks 1/2/3 then blue gradient for 4..20
blue_ramp <- colorRampPalette(c("#deebf7", "#9ecae1", "#3182bd"))(max_rank - 3)
rank_colors <- c("#e34a33", "#fdbb84", "#fee8c8", blue_ramp)
names(rank_colors) <- 1:max_rank

female_heatmap_improved <- female_evolution_matrix %>%
  ggplot(aes(x = year, y = prenom, fill = factor(custom_rank))) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = ifelse(is.na(custom_rank), "", custom_rank)), 
            color = "black", fontface = "bold", size = 3) +
  # Manual color scale with exact mapping
  scale_fill_manual(
    values = rank_colors,
    na.value = "grey90",
    name = "Rank"
  ) +
  scale_y_discrete(limits = rev(levels(female_evolution_matrix$prenom))) +
  labs(title = "Female Names Evolution - Last 10 Years (Current Top 20)",
       x = "Year", y = "Name") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank())

# Convert to plotly
female_heatmap_plotly <- ggplotly(female_heatmap_improved, 
                                  tooltip = c("x", "y", "fill")) %>%
  layout(hovermode = "closest")

female_heatmap_plotly
```

## Store Results for Text Generation

```{r store-results-ch2}
# Store leader analysis results
results$leaders <- list(
  male_leader = list(
    name = current_male_leader,
    years_as_top = male_leader_summary$total_years_as_leader,
    years_list = male_leader_years$year
  ),
  female_leader = list(
    name = current_female_leader,
    years_as_top = female_leader_summary$total_years_as_leader,
    years_list = female_leader_years$year
  )
)

# Store top 20 evolution data
results$evolution <- list(
  male_current_top20 = male_current_top20,
  female_current_top20 = female_current_top20
)

cat("✅ Chapter 2 results stored\n")
cat("Male leader:", current_male_leader, "- Years as #1:", male_leader_summary$total_years_as_leader, "\n")
cat("Female leader:", current_female_leader, "- Years as #1:", female_leader_summary$total_years_as_leader, "\n")
```

## ------------------------------------------------------------------------

# Chapter 3 - Biggest Changes Year-over-Year

```{r setup-ch3, include=FALSE}
library(tidyverse)
library(DT)
```

## Data Preparation for Changes Analysis

```{r changes-data-prep}
# Get rankings for comparison year and current year (top 200 each year)
rankings_comparison_year <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         year == comparison_year,
         custom_rank <= top_n_analysis) %>%
  select(prenom, gender, value, custom_rank) %>%
  rename(rank_prev = custom_rank, count_prev = value)

rankings_current_year <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse",
         year == data_year,
         custom_rank <= top_n_analysis) %>%
  select(prenom, gender, value, custom_rank) %>%
  rename(rank_current = custom_rank, count_current = value)

# Combine both years to calculate changes
rank_changes <- full_join(rankings_comparison_year, rankings_current_year, 
                         by = c("prenom", "gender")) %>%
  mutate(
    rank_prev = ifelse(is.na(rank_prev), top_n_analysis + 1, rank_prev),
    rank_current = ifelse(is.na(rank_current), top_n_analysis + 1, rank_current),
    rank_change = rank_prev - rank_current,  # Positive = gained positions (climbed up)
    count_change = count_current - count_prev,
    # Status categorization
    status = case_when(
      is.na(count_prev) & !is.na(count_current) ~ "New Entry",
      !is.na(count_prev) & is.na(count_current) ~ "Dropped Out", 
      TRUE ~ "Continued"
    )
  ) %>%
  filter(!is.na(prenom))

cat("✅ Changes analysis data prepared\n")
cat("Total names analyzed:", nrow(rank_changes), "\n")
```

## 3.1 Biggest Climbers

### Male Biggest Climbers

```{r male-climbers}
# Male names with biggest positive rank changes
male_climbers <- rank_changes %>%
  filter(gender == "male", 
         status == "Continued",
         rank_change > 0) %>%
  arrange(desc(rank_change)) %>%
  slice_head(n = 10) %>%
  select(prenom, rank_prev, rank_current, rank_change, count_prev, count_current, count_change)

# Print results
print("Male Names - Biggest Climbers:")
print(male_climbers)

# Display as datatable
datatable(male_climbers, 
          colnames = c("Name", "Rank Previous", "Rank Current", "Rank Change", 
                      "Count Previous", "Count Current", "Count Change"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Male Names with Biggest Rank Gains", comparison_year, "→", data_year))
```

### Female Biggest Climbers

```{r female-climbers}
# Female names with biggest positive rank changes
female_climbers <- rank_changes %>%
  filter(gender == "female", 
         status == "Continued",
         rank_change > 0) %>%
  arrange(desc(rank_change)) %>%
  slice_head(n = 10) %>%
  select(prenom, rank_prev, rank_current, rank_change, count_prev, count_current, count_change)

# Print results
print("Female Names - Biggest Climbers:")
print(female_climbers)

# Display as datatable
datatable(female_climbers, 
          colnames = c("Name", "Rank Previous", "Rank Current", "Rank Change", 
                      "Count Previous", "Count Current", "Count Change"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Female Names with Biggest Rank Gains", comparison_year, "→", data_year))
```

## 3.2 Biggest Fallers

### Male Biggest Fallers

```{r male-fallers}
# Male names with biggest negative rank changes
male_fallers <- rank_changes %>%
  filter(gender == "male", 
         status == "Continued",
         rank_change < 0) %>%
  arrange(rank_change) %>%
  slice_head(n = 10) %>%
  select(prenom, rank_prev, rank_current, rank_change, count_prev, count_current, count_change)

# Print results
print("Male Names - Biggest Fallers:")
print(male_fallers)

# Display as datatable
datatable(male_fallers, 
          colnames = c("Name", "Rank Previous", "Rank Current", "Rank Change", 
                      "Count Previous", "Count Current", "Count Change"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Male Names with Biggest Rank Losses", comparison_year, "→", data_year))
```

### Female Biggest Fallers

```{r female-fallers}
# Female names with biggest negative rank changes
female_fallers <- rank_changes %>%
  filter(gender == "female", 
         status == "Continued",
         rank_change < 0) %>%
  arrange(rank_change) %>%
  slice_head(n = 10) %>%
  select(prenom, rank_prev, rank_current, rank_change, count_prev, count_current, count_change)

# Print results
print("Female Names - Biggest Fallers:")
print(female_fallers)

# Display as datatable
datatable(female_fallers, 
          colnames = c("Name", "Rank Previous", "Rank Current", "Rank Change", 
                      "Count Previous", "Count Current", "Count Change"),
          options = list(dom = 't', pageLength = 10),
          caption = paste("Female Names with Biggest Rank Losses", comparison_year, "→", data_year))
```

## 3.3 New Entries and Exits from Top 100

### New Entries to Top 100

#### Male New Entries

```{r male-new-entries}
# Male names entering top 100
male_new_entries <- rank_changes %>%
  filter(gender == "male",
         rank_current <= top_n_display,
         (is.na(rank_prev) | rank_prev > top_n_display)) %>%
  arrange(rank_current) %>%
  select(prenom, rank_current, count_current)

# Print results
print("Male Names - New Entries to Top 100:")
print(male_new_entries)

# Display as datatable
datatable(male_new_entries, 
          colnames = c("Name", "Current Rank", "Current Count"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Male Names Entering Top 100 in", data_year))
```

#### Female New Entries

```{r female-new-entries}
# Female names entering top 100
female_new_entries <- rank_changes %>%
  filter(gender == "female",
         rank_current <= top_n_display,
         (is.na(rank_prev) | rank_prev > top_n_display)) %>%
  arrange(rank_current) %>%
  select(prenom, rank_current, count_current)

# Print results
print("Female Names - New Entries to Top 100:")
print(female_new_entries)

# Display as datatable
datatable(female_new_entries, 
          colnames = c("Name", "Current Rank", "Current Count"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Female Names Entering Top 100 in", data_year))
```

### Exits from Top 100

#### Male Exits

```{r male-exits}
# Male names exiting top 100
male_exits <- rank_changes %>%
  filter(gender == "male",
         rank_prev <= top_n_display,
         (is.na(rank_current) | rank_current > top_n_display)) %>%
  arrange(rank_prev) %>%
  select(prenom, rank_prev, count_prev)

# Print results
print("Male Names - Exits from Top 100:")
print(male_exits)

# Display as datatable
datatable(male_exits, 
          colnames = c("Name", "Previous Rank", "Previous Count"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Male Names Exiting Top 100 in", data_year))
```

#### Female Exits

```{r female-exits}
# Female names exiting top 100
female_exits <- rank_changes %>%
  filter(gender == "female",
         rank_prev <= top_n_display,
         (is.na(rank_current) | rank_current > top_n_display)) %>%
  arrange(rank_prev) %>%
  select(prenom, rank_prev, count_prev)

# Print results
print("Female Names - Exits from Top 100:")
print(female_exits)

# Display as datatable
datatable(female_exits, 
          colnames = c("Name", "Previous Rank", "Previous Count"),
          options = list(dom = 't', pageLength = 15),
          caption = paste("Female Names Exiting Top 100 in", data_year))
```

## Store Results for Text Generation

```{r store-results-ch3}
# Store biggest changes results
results$changes <- list(
  male_biggest_climber = if(nrow(male_climbers) > 0) {
    list(name = male_climbers$prenom[1], rank_change = male_climbers$rank_change[1])
  } else { list(name = NA, rank_change = 0) },
  
  female_biggest_climber = if(nrow(female_climbers) > 0) {
    list(name = female_climbers$prenom[1], rank_change = female_climbers$rank_change[1])
  } else { list(name = NA, rank_change = 0) },
  
  male_biggest_faller = if(nrow(male_fallers) > 0) {
    list(name = male_fallers$prenom[1], rank_change = abs(male_fallers$rank_change[1]))
  } else { list(name = NA, rank_change = 0) },
  
  female_biggest_faller = if(nrow(female_fallers) > 0) {
    list(name = female_fallers$prenom[1], rank_change = abs(female_fallers$rank_change[1]))
  } else { list(name = NA, rank_change = 0) },
  
  new_entries = list(
    male = male_new_entries$prenom,
    female = female_new_entries$prenom
  ),
  
  exits = list(
    male = male_exits$prenom,
    female = female_exits$prenom
  )
)

cat("✅ Chapter 3 results stored\n")
cat("Top climbers:", results$changes$male_biggest_climber$name, "(M),", results$changes$female_biggest_climber$name, "(F)\n")
cat("Top fallers:", results$changes$male_biggest_faller$name, "(M),", results$changes$female_biggest_faller$name, "(F)\n")
```

## ------------------------------------------------------------------------

# Chapter 4 - Total Population Analysis

```{r setup-ch4, include=FALSE}
library(tidyverse)
library(DT)
```

## Data Preparation for Population Analysis

```{r population-data-prep}
# Get current and previous year population data
all_names_current <- bind_rows(
  get(paste0("all_female_names_ch_", data_year)),
  get(paste0("all_male_names_ch_", data_year))
)

all_names_previous <- bind_rows(
  get(paste0("all_female_names_ch_", comparison_year)),
  get(paste0("all_male_names_ch_", comparison_year))
)

# Group by name and gender for current year
population_current <- all_names_current %>%
  group_by(firstname, gender) %>%
  summarise(total_population_current = sum(value), .groups = 'drop') %>%
  arrange(desc(total_population_current))

# Group by name and gender for previous year
population_previous <- all_names_previous %>%
  group_by(firstname, gender) %>%
  summarise(total_population_previous = sum(value), .groups = 'drop')

# Combine and calculate changes
population_changes <- full_join(population_previous, population_current, 
                               by = c("firstname", "gender")) %>%
  mutate(
    total_population_current = ifelse(is.na(total_population_current), 0, total_population_current),
    total_population_previous = ifelse(is.na(total_population_previous), 0, total_population_previous),
    population_change = total_population_current - total_population_previous
  ) %>%
  filter(total_population_current > 0) %>%  # Keep only names still in population
  arrange(desc(total_population_current))

cat("✅ Population analysis data prepared\n")
cat("Total unique names in current population:", nrow(population_changes), "\n")
```

## 4.1 Most Common Names in Total Population

### Male Most Common Names

```{r male-most-common}
# Top 20 most common male names in total population
male_most_common <- population_changes %>%
  filter(gender == "male") %>%
  slice_head(n = 20) %>%
  select(firstname, total_population_current, total_population_previous, population_change)

# Print results
print("Male Names - Most Common in Total Population:")
print(male_most_common)

# Display as datatable
datatable(male_most_common, 
          colnames = c("Name", paste("Total", data_year), paste("Total", comparison_year), "Change"),
          options = list(dom = 't', pageLength = 20),
          caption = paste("Most Common Male Names in Swiss Population", data_year)) %>%
  formatRound(c("total_population_current", "total_population_previous", "population_change"), 
              digits = 0, mark = "'")
```

### Female Most Common Names

```{r female-most-common}
# Top 20 most common female names in total population
female_most_common <- population_changes %>%
  filter(gender == "female") %>%
  slice_head(n = 20) %>%
  select(firstname, total_population_current, total_population_previous, population_change)

# Print results
print("Female Names - Most Common in Total Population:")
print(female_most_common)

# Display as datatable
datatable(female_most_common, 
          colnames = c("Name", paste("Total", data_year), paste("Total", comparison_year), "Change"),
          options = list(dom = 't', pageLength = 20),
          caption = paste("Most Common Female Names in Swiss Population", data_year)) %>%
  formatRound(c("total_population_current", "total_population_previous", "population_change"), 
              digits = 0, mark = "'")
```

## 4.2 Specific Name Evolution Analysis

### Traditional Leaders Evolution

```{r traditional-leaders}
# Look for Maria and Daniel specifically (traditional most common names)
traditional_names <- c("Maria", "Daniel")

traditional_evolution <- population_changes %>%
  filter(firstname %in% traditional_names) %>%
  select(firstname, gender, total_population_current, total_population_previous, population_change) %>%
  arrange(desc(total_population_current))

# Print results
print("Evolution of Traditional Most Common Names:")
print(traditional_evolution)

# Display as datatable
datatable(traditional_evolution, 
          colnames = c("Name", "Gender", paste("Total", data_year), paste("Total", comparison_year), "Change"),
          options = list(dom = 't', pageLength = 10),
          caption = "Evolution of Traditionally Most Common Names") %>%
  formatRound(c("total_population_current", "total_population_previous", "population_change"), 
              digits = 0, mark = "'")
```

### Biggest Population Changes

```{r biggest-population-changes}
# Names with biggest absolute population changes (positive and negative)
biggest_increases <- population_changes %>%
  filter(population_change > 0) %>%
  arrange(desc(population_change)) %>%
  slice_head(n = 10) %>%
  select(firstname, gender, total_population_current, total_population_previous, population_change)

biggest_decreases <- population_changes %>%
  filter(population_change < 0) %>%
  arrange(population_change) %>%
  slice_head(n = 10) %>%
  select(firstname, gender, total_population_current, total_population_previous, population_change)

# Print results
print("Names with Biggest Population Increases:")
print(biggest_increases)

print("Names with Biggest Population Decreases:")
print(biggest_decreases)

# Display as datatables
datatable(biggest_increases, 
          colnames = c("Name", "Gender", paste("Total", data_year), paste("Total", comparison_year), "Change"),
          options = list(dom = 't', pageLength = 10),
          caption = "Names with Biggest Population Increases") %>%
  formatRound(c("total_population_current", "total_population_previous", "population_change"), 
              digits = 0, mark = "'")

datatable(biggest_decreases, 
          colnames = c("Name", "Gender", paste("Total", data_year), paste("Total", comparison_year), "Change"),
          options = list(dom = 't', pageLength = 10),
          caption = "Names with Biggest Population Decreases") %>%
  formatRound(c("total_population_current", "total_population_previous", "population_change"), 
              digits = 0, mark = "'")
```

## Store Results for Text Generation

```{r store-results-ch4}
# Store population analysis results
results$population <- list(
  most_common = list(
    male_top = male_most_common$firstname[1:3],
    female_top = female_most_common$firstname[1:3],
    male_top_counts = male_most_common$total_population_current[1:3],
    female_top_counts = female_most_common$total_population_current[1:3]
  ),
  
  traditional_leaders = list(
    maria_current = if("Maria" %in% traditional_evolution$firstname) {
      traditional_evolution %>% filter(firstname == "Maria") %>% pull(total_population_current)
    } else { NA },
    maria_previous = if("Maria" %in% traditional_evolution$firstname) {
      traditional_evolution %>% filter(firstname == "Maria") %>% pull(total_population_previous)
    } else { NA },
    daniel_current = if("Daniel" %in% traditional_evolution$firstname) {
      traditional_evolution %>% filter(firstname == "Daniel") %>% pull(total_population_current)
    } else { NA },
    daniel_previous = if("Daniel" %in% traditional_evolution$firstname) {
      traditional_evolution %>% filter(firstname == "Daniel") %>% pull(total_population_previous)
    } else { NA }
  ),
  
  biggest_changes = list(
    biggest_increase = if(nrow(biggest_increases) > 0) {
      list(name = biggest_increases$firstname[1], 
           gender = biggest_increases$gender[1],
           change = biggest_increases$population_change[1])
    } else { list(name = NA, gender = NA, change = 0) },
    
    biggest_decrease = if(nrow(biggest_decreases) > 0) {
      list(name = biggest_decreases$firstname[1], 
           gender = biggest_decreases$gender[1],
           change = abs(biggest_decreases$population_change[1]))
    } else { list(name = NA, gender = NA, change = 0) }
  )
)

cat("✅ Chapter 4 results stored\n")
cat("Most common names - Male:", paste(results$population$most_common$male_top, collapse = ", "), "\n")
cat("Most common names - Female:", paste(results$population$most_common$female_top, collapse = ", "), "\n")
```

## ------------------------------------------------------------------------

# Chapter 5 - Complementary Analyses

```{r setup-ch5, include=FALSE}
library(tidyverse)
library(DT)
library(plotly)
```

## 5.1 Name Diversity Evolution

```{r diversity-analysis}
# Calculate diversity metrics by year (using PX data for newborns)
diversity_evolution <- px_names_with_custom_ranks %>%
  filter(region_linguistique_canton == "Suisse") %>%
  group_by(year, gender) %>%
  summarise(
    total_births = sum(value, na.rm = TRUE),
    unique_names = n_distinct(prenom),
    top10_births = sum(value[custom_rank <= 10], na.rm = TRUE),
    top10_concentration = (top10_births / total_births) * 100,
    .groups = 'drop'
  )

# Print results for male and female separately
diversity_male <- diversity_evolution %>% 
  filter(gender == "male") %>%
  select(year, total_births, unique_names, top10_concentration)

diversity_female <- diversity_evolution %>% 
  filter(gender == "female") %>%
  select(year, total_births, unique_names, top10_concentration)

print("Name Diversity Evolution - Male:")
print(diversity_male)

print("Name Diversity Evolution - Female:")
print(diversity_female)
```

```{r diversity-tables}
# Display as datatables
datatable(diversity_male, 
          colnames = c("Year", "Total Births", "Unique Names", "Top 10 Concentration (%)"),
          options = list(dom = 't', pageLength = 25),
          caption = "Name Diversity Evolution - Male Names") %>%
  formatRound(c("top10_concentration"), digits = 1)

datatable(diversity_female, 
          colnames = c("Year", "Total Births", "Unique Names", "Top 10 Concentration (%)"),
          options = list(dom = 't', pageLength = 25),
          caption = "Name Diversity Evolution - Female Names") %>%
  formatRound(c("top10_concentration"), digits = 1)
```

## 5.2 Average Name Length Analysis

### Name Length by Birth Year

```{r name-length-by-birth}
# Calculate average name length by birth year using POPULATION data (CORRECTED)
length_by_birth_year <- all_names_current %>%
  mutate(name_length = nchar(firstname)) %>%
  group_by(yearofbirth, gender) %>%
  summarise(
    avg_length = mean(name_length, na.rm = TRUE),  # Simple mean of unique names
    total_people = sum(value, na.rm = TRUE),
    unique_names = n_distinct(firstname),
    .groups = 'drop'
  ) %>%
  filter(yearofbirth >= 1950, total_people >= 100) %>%  # Filter for reliable data
  arrange(yearofbirth)

# Calculate overall average by year for both genders combined
length_by_birth_year_combined <- length_by_birth_year %>%
  group_by(yearofbirth) %>%
  summarise(
    avg_length_combined = mean(avg_length),  # Simple mean of male/female averages
    .groups = 'drop'
  )

# Combine data for visualization
length_data_complete <- length_by_birth_year %>%
  left_join(length_by_birth_year_combined, by = "yearofbirth")

# Print recent years data
recent_length <- length_data_complete %>%
  filter(yearofbirth >= data_year - 10) %>%
  arrange(desc(yearofbirth))

print("Average Name Length - Recent Birth Years (Population Data):")
print(recent_length)
```

```{r length-table}
# Display as datatable
datatable(recent_length, 
          colnames = c("Birth Year", "Gender", "Avg Length", "Total People", "Combined Avg"),
          options = list(dom = 't', pageLength = 25),
          caption = "Average Name Length by Birth Year (Population Data)") %>%
  formatRound(c("avg_length", "avg_length_combined"), digits = 2) %>%
  formatRound(c("total_people"), digits = 0, mark = "'")
```

### Interactive Name Length Evolution Chart

```{r name-length-chart}
# Create interactive plotly chart
length_plot <- ggplot(length_data_complete, aes(x = yearofbirth)) +
  geom_line(aes(y = avg_length, color = gender, group = gender), size = 1.2) +
  geom_line(aes(y = avg_length_combined), color = "black", linetype = "dashed", size = 1) +
  scale_color_manual(values = c("female" = "#e34a33", "male" = "#3182bd"), 
                     name = "Gender") +
  labs(title = "Average Name Length Evolution by Birth Year",
       x = "Birth Year",
       y = "Average Name Length (characters)",
       subtitle = "Dashed line shows combined average") +
  theme_minimal() +
  theme(legend.position = "bottom")

# Convert to plotly for interactivity
length_plot_interactive <- ggplotly(length_plot, tooltip = c("x", "y", "colour")) %>%
  layout(hovermode = "x unified")

length_plot_interactive
```

### Current Year Name Length Analysis

```{r current-year-length}
# Calculate name length for current year births using POPULATION data (CORRECTED)
current_year_length <- all_names_current %>%
  filter(yearofbirth == data_year) %>%
  mutate(name_length = nchar(firstname)) %>%
  group_by(gender) %>%
  summarise(
    avg_length = mean(name_length, na.rm = TRUE),  # Simple mean of unique names
    total_people = sum(value, na.rm = TRUE),
    unique_names = n_distinct(firstname),
    .groups = 'drop'
  )

# Overall average for current year
current_year_overall <- all_names_current %>%
  filter(yearofbirth == data_year) %>%
  mutate(name_length = nchar(firstname)) %>%
  summarise(
    avg_length_overall = mean(name_length, na.rm = TRUE),  # Simple mean of unique names
    total_people = sum(value, na.rm = TRUE),
    unique_names = n_distinct(firstname)
  )

# Combine results
current_length_summary <- current_year_length %>%
  bind_rows(tibble(gender = "Overall", 
                   avg_length = current_year_overall$avg_length_overall,
                   total_people = current_year_overall$total_people,
                   unique_names = current_year_overall$unique_names))

print(paste("Average Name Length Analysis for", data_year, "Births (Population Data):"))
print(current_length_summary)
```

```{r current-length-table}
# Display as datatable
datatable(
  current_length_summary, 
  colnames = c("Gender", "Average Length", "Total People", "Unique Names"),
  options = list(dom = 't', pageLength = 10),
  caption = paste("Average Name Length for", data_year, "Newborns")
) %>%
  formatRound(c("avg_length"), digits = 2) %>%
  formatRound(c("total_people"), digits = 0, mark = "'") %>%
  formatRound(c("unique_names"), digits = 0, mark = "'")
```

## Store Results for Text Generation

```{r store-results-ch5}
# Store complementary analyses results
results$complementary <- list(
  diversity = list(
    male_unique_names = diversity_male %>% filter(year == data_year) %>% pull(unique_names),
    female_unique_names = diversity_female %>% filter(year == data_year) %>% pull(unique_names),
    male_top10_concentration = diversity_male %>% filter(year == data_year) %>% pull(top10_concentration),
    female_top10_concentration = diversity_female %>% filter(year == data_year) %>% pull(top10_concentration)
  ),
  
  name_length = list(
    current_year_overall = round(current_year_overall$avg_length_overall, 2),
    current_year_male = round(current_length_summary %>% filter(gender == "male") %>% pull(avg_length), 2),
    current_year_female = round(current_length_summary %>% filter(gender == "female") %>% pull(avg_length), 2),
    trend_start_year = min(length_data_complete$yearofbirth),
    trend_end_year = max(length_data_complete$yearofbirth)
  )
)

cat("✅ Chapter 5 results stored\n")
cat("Current year average name length:", results$complementary$name_length$current_year_overall, "characters\n")
cat("Male:", results$complementary$name_length$current_year_male, 
    "/ Female:", results$complementary$name_length$current_year_female, "\n")
```

## ------------------------------------------------------------------------

# Chapter 6 - Automated Text Generation

```{r setup-ch6, include=FALSE}
library(tidyverse)
library(glue)
```

## Generate Article Text

```{r generate-text}
# Extract key variables for text generation
national_male_1 <- results$rankings$national$male[1]
national_male_2 <- results$rankings$national$male[2] 
national_male_3 <- results$rankings$national$male[3]

national_female_1 <- results$rankings$national$female[1]
national_female_2 <- results$rankings$national$female[2]
national_female_3 <- results$rankings$national$female[3]

# Regional leaders
alemanique_male_1 <- results$rankings$regional$alemanique$male[1]
alemanique_female_1 <- results$rankings$regional$alemanique$female[1]
romande_male_1 <- results$rankings$regional$romande$male[1] 
romande_female_1 <- results$rankings$regional$romande$female[1]
italienne_male_1 <- results$rankings$regional$italienne$male[1]
italienne_female_1 <- results$rankings$regional$italienne$female[1]

# Leaders analysis
male_leader_name <- results$leaders$male_leader$name
male_leader_years <- results$leaders$male_leader$years_as_top
female_leader_name <- results$leaders$female_leader$name
female_leader_years <- results$leaders$female_leader$years_as_top

# Changes analysis
male_biggest_climber <- results$changes$male_biggest_climber$name
male_climber_gain <- results$changes$male_biggest_climber$rank_change
female_biggest_climber <- results$changes$female_biggest_climber$name
female_climber_gain <- results$changes$female_biggest_climber$rank_change

male_biggest_faller <- results$changes$male_biggest_faller$name
male_faller_loss <- results$changes$male_biggest_faller$rank_change
female_biggest_faller <- results$changes$female_biggest_faller$name
female_faller_loss <- results$changes$female_biggest_faller$rank_change

# New entries
new_entries_sample <- c(results$changes$new_entries$male[1:2], results$changes$new_entries$female[1:2])
new_entries_text <- paste(new_entries_sample[!is.na(new_entries_sample)], collapse = ", ")

# Population analysis
most_common_male <- results$population$most_common$male_top[1]
most_common_female <- results$population$most_common$female_top[1]
most_common_male_count <- results$population$most_common$male_top_counts[1]
most_common_female_count <- results$population$most_common$female_top_counts[1]

# Traditional leaders evolution
maria_current <- results$population$traditional_leaders$maria_current
maria_previous <- results$population$traditional_leaders$maria_previous
maria_change <- maria_current - maria_previous

daniel_current <- results$population$traditional_leaders$daniel_current
daniel_previous <- results$population$traditional_leaders$daniel_previous
daniel_change <- daniel_current - daniel_previous

# Name length analysis (with fallback if missing)
if ("complementary" %in% names(results) && "name_length" %in% names(results$complementary)) {
  avg_length_overall <- results$complementary$name_length$current_year_overall
  avg_length_female <- results$complementary$name_length$current_year_female
  avg_length_male <- results$complementary$name_length$current_year_male
} else {
  avg_length_overall <- "5.6"
  avg_length_female <- "5.7" 
  avg_length_male <- "5.5"
  cat("Warning: Name length data not found, using fallback values\n")
}

# Generate HTML versions for CMS copy-paste
article_html_fr <- glue("
<p><strong>Quels étaient les prénoms les plus populaires en {data_year} ? Et comment les tendances ont-elles évolué au fil des décennies ? Découvrez-le grâce à notre outil interactif.</strong></p>

<p>Voici les stars de {data_year} : <strong>{national_female_1}</strong> et <strong>{national_male_1}</strong> sont les prénoms qui ont été donnés le plus souvent aux nouveau-nés en Suisse l'an passé.</p>

<p><strong>{national_male_1}</strong> garde la première place, comme lors d'années précédentes où il dominait les classements. Le top 3 est resté stable : <strong>{national_male_1}</strong> est encore suivi par <strong>{national_male_2}</strong> et par <strong>{national_male_3}</strong> au niveau national.</p>

<p>Chez les filles, <strong>{national_female_1}</strong> reprend la première place, suivie par <strong>{national_female_2}</strong> et par <strong>{national_female_3}</strong>. Cela représente les tendances de préférences actuelles pour les prénoms féminins.</p>

<p>Quels sont les prénoms qui grimpent le plus ? Il y a <strong>{female_biggest_climber}</strong> chez les filles et <strong>{male_biggest_climber}</strong> chez les garçons. Ce sont les prénoms qui ont gagné le plus de places dans le classement. Ils ont progressé respectivement de {female_climber_gain} et {male_climber_gain} places entre {comparison_year} et {data_year}.</p>

<p>Parmi les prénoms qui ont dégringolé, il y a <strong>{female_biggest_faller}</strong> chez les filles et <strong>{male_biggest_faller}</strong> chez les garçons. Ils ont respectivement perdu plus de {female_faller_loss} et {male_faller_loss} places.</p>

<p>Parmi les nouveaux venus dans le top 100 des prénoms les plus populaires pour les nouveaux-nés, on trouve désormais {new_entries_text}.</p>

<p>Les prénoms les plus populaires en {data_year} ne sont pas les mêmes partout : en Suisse alémanique, <strong>{alemanique_male_1}</strong> et <strong>{alemanique_female_1}</strong> occupent la première place, mais en Suisse romande, ce sont <strong>{romande_male_1}</strong> et <strong>{romande_female_1}</strong> qui sont en tête du classement. En Suisse italienne, ce sont <strong>{italienne_male_1}</strong> et <strong>{italienne_female_1}</strong> qui occupent la première place du podium.</p>

<p>Même si le prénom <strong>{most_common_female}</strong> est en perte de vitesse, il reste le prénom féminin le plus répandu dans l'ensemble de la population, avec près de {format(most_common_female_count, big.mark = ' ')} femmes portant ce prénom, contre {format(most_common_female_count - abs(maria_change), big.mark = ' ')} l'année précédente.</p>

<p>Chez les hommes, <strong>{most_common_male}</strong> est toujours le prénom le plus fréquent en Suisse. Près de {format(most_common_male_count, big.mark = ' ')} hommes et garçons s'appellent ainsi, contre {format(daniel_previous, big.mark = ' ')} en {comparison_year}.</p>

<p>Avec <strong>{national_female_1}</strong> et <strong>{national_male_1}</strong>, ce sont à nouveau deux prénoms courts qui ont été attribués le plus souvent en {data_year}. La longueur moyenne des prénoms des personnes nées en {data_year} est de {avg_length_overall} caractères. Chez les femmes, cette longueur est légèrement plus importante ({avg_length_female} caractères) que chez les hommes ({avg_length_male}).</p>

<p>Les personnes plus âgées ont tendance à avoir des prénoms plus longs.</p>
")

article_html_de <- glue("
<p><strong>Welches waren die beliebtesten Vornamen im Jahr {data_year}? Und wie haben sich die Trends über die Jahrzehnte entwickelt? Entdecken Sie es mit unserem interaktiven Tool.</strong></p>

<p>Hier sind die Stars von {data_year}: <strong>{national_female_1}</strong> und <strong>{national_male_1}</strong> sind die Namen, die Neugeborenen in der Schweiz im vergangenen Jahr am häufigsten gegeben wurden.</p>

<p><strong>{national_male_1}</strong> behält den ersten Platz, wie in früheren Jahren, in denen er die Rankings dominierte. Die Top 3 blieben stabil: <strong>{national_male_1}</strong> wird noch immer von <strong>{national_male_2}</strong> und <strong>{national_male_3}</strong> auf nationaler Ebene gefolgt.</p>

<p>Bei den Mädchen nimmt <strong>{national_female_1}</strong> den ersten Platz ein, gefolgt von <strong>{national_female_2}</strong> und <strong>{national_female_3}</strong>. Dies repräsentiert die aktuellen Präferenztrends für weibliche Vornamen.</p>

<p>Welche Namen steigen am meisten? Da sind <strong>{female_biggest_climber}</strong> bei den Mädchen und <strong>{male_biggest_climber}</strong> bei den Jungen. Das sind die Namen, die die meisten Plätze im Ranking gewonnen haben. Sie sind zwischen {comparison_year} und {data_year} um {female_climber_gain} bzw. {male_climber_gain} Plätze gestiegen.</p>

<p>Unter den Namen, die gefallen sind, gibt es <strong>{female_biggest_faller}</strong> bei den Mädchen und <strong>{male_biggest_faller}</strong> bei den Jungen. Sie haben jeweils mehr als {female_faller_loss} bzw. {male_faller_loss} Plätze verloren.</p>

<p>Unter den Neueinsteigern in die Top 100 der beliebtesten Namen für Neugeborene finden wir nun {new_entries_text}.</p>

<p>Die beliebtesten Namen in {data_year} sind nicht überall gleich: In der Deutschschweiz belegen <strong>{alemanique_male_1}</strong> und <strong>{alemanique_female_1}</strong> den ersten Platz, aber in der Romandie stehen <strong>{romande_male_1}</strong> und <strong>{romande_female_1}</strong> an der Spitze der Rangliste. In der italienischsprachigen Schweiz belegen <strong>{italienne_male_1}</strong> und <strong>{italienne_female_1}</strong> den ersten Platz auf dem Podium.</p>

<p>Auch wenn der Name <strong>{most_common_female}</strong> an Boden verliert, bleibt er der am weitesten verbreitete weibliche Vorname in der Gesamtbevölkerung, mit fast {format(most_common_female_count, big.mark = ' ')} Frauen, die diesen Namen tragen, gegenüber {format(most_common_female_count - abs(maria_change), big.mark = ' ')} im Vorjahr.</p>

<p>Bei den Männern ist <strong>{most_common_male}</strong> immer noch der häufigste Name in der Schweiz. Fast {format(most_common_male_count, big.mark = ' ')} Männer und Jungen heissen so, gegenüber {format(daniel_previous, big.mark = ' ')} in {comparison_year}.</p>

<p>Mit <strong>{national_female_1}</strong> und <strong>{national_male_1}</strong> wurden im Jahr {data_year} erneut zwei kurze Namen am häufigsten vergeben. Die durchschnittliche Vornamenslänge der im Jahr {data_year} Geborenen liegt bei {avg_length_overall} Zeichen. Bei Frauen ist die Länge mit {avg_length_female} Zeichen etwas umfangreicher als bei den Männern mit {avg_length_male}.</p>

<p>Ältere Menschen haben tendenziell längere Vornamen.</p>
")

article_html_en <- glue("
<p><strong>What were the most popular first names in {data_year}? And how have trends evolved over the decades? Discover it with our interactive tool.</strong></p>

<p>Here are the stars of {data_year}: <strong>{national_female_1}</strong> and <strong>{national_male_1}</strong> are the names that were most often given to newborns in Switzerland last year.</p>

<p><strong>{national_male_1}</strong> maintains first place, as in previous years when it dominated the rankings. The top 3 has remained stable: <strong>{national_male_1}</strong> is still followed by <strong>{national_male_2}</strong> and <strong>{national_male_3}</strong> at the national level.</p>

<p>Among girls, <strong>{national_female_1}</strong> takes first place, followed by <strong>{national_female_2}</strong> and <strong>{national_female_3}</strong>. This represents the current preference trends for female names.</p>

<p>What are the names that are climbing the most? There are <strong>{female_biggest_climber}</strong> among girls and <strong>{male_biggest_climber}</strong> among boys. These are the names that have gained the most places in the rankings. They progressed by {female_climber_gain} and {male_climber_gain} places respectively between {comparison_year} and {data_year}.</p>

<p>Among the names that have fallen, there are <strong>{female_biggest_faller}</strong> among girls and <strong>{male_biggest_faller}</strong> among boys. They lost more than {female_faller_loss} and {male_faller_loss} places respectively.</p>

<p>Among the newcomers in the top 100 of the most popular names for newborns, we now find {new_entries_text}.</p>

<p>The most popular names in {data_year} are not the same everywhere: in German-speaking Switzerland, <strong>{alemanique_male_1}</strong> and <strong>{alemanique_female_1}</strong> occupy first place, but in French-speaking Switzerland, <strong>{romande_male_1}</strong> and <strong>{romande_female_1}</strong> are at the top of the rankings. In Italian-speaking Switzerland, <strong>{italienne_male_1}</strong> and <strong>{italienne_female_1}</strong> occupy first place on the podium.</p>

<p>Even if the name <strong>{most_common_female}</strong> is losing ground, it remains the most widespread female name in the entire population, with nearly {format(most_common_female_count, big.mark = ',')} women bearing this name, compared to {format(most_common_female_count - abs(maria_change), big.mark = ',')} the previous year.</p>

<p>Among men, <strong>{most_common_male}</strong> is still the most frequent name in Switzerland. Nearly {format(most_common_male_count, big.mark = ',')} men and boys are called this, compared to {format(daniel_previous, big.mark = ',')} in {comparison_year}.</p>

<p>With <strong>{national_female_1}</strong> and <strong>{national_male_1}</strong>, these are once again two short names that were most often attributed in {data_year}. The average length of first names of people born in {data_year} is {avg_length_overall} characters. Among women, this length is slightly longer ({avg_length_female} characters) than among men ({avg_length_male}).</p>

<p>Older people tend to have longer first names.</p>
")

cat("GENERATED HTML TEXTS (Ready for CMS):\n")
cat("=" %>% rep(60) %>% paste(collapse = ""), "\n\n")

cat("🇫🇷 FRANÇAIS (HTML)\n")
cat("-" %>% rep(30) %>% paste(collapse = ""), "\n")
cat(article_html_fr)
cat("\n\n")

cat("🇩🇪 DEUTSCH (HTML)\n") 
cat("-" %>% rep(30) %>% paste(collapse = ""), "\n")
cat(article_html_de)
cat("\n\n")

cat("🇬🇧 ENGLISH (HTML)\n")
cat("-" %>% rep(30) %>% paste(collapse = ""), "\n")
cat(article_html_en)

cat("\n\n", "=" %>% rep(60) %>% paste(collapse = ""), "\n")

# Also save HTML versions to files for easy access
writeLines(article_html_fr, file.path(output_dir, paste0("article_fr_", data_year, ".html")))
writeLines(article_html_de, file.path(output_dir, paste0("article_de_", data_year, ".html")))
writeLines(article_html_en, file.path(output_dir, paste0("article_en_", data_year, ".html")))

cat("\n📁 HTML files saved in 'output/' directory for easy copy-paste\n")

# Copy to clipboard function (works on different OS)
copy_to_clipboard <- function(text, lang) {
  tryCatch({
    if (Sys.info()["sysname"] == "Darwin") {  # macOS
      writeLines(text, pipe("pbcopy"))
    } else if (Sys.info()["sysname"] == "Windows") {  # Windows
      writeLines(text, "clipboard")
    } else {  # Linux
      writeLines(text, pipe("xclip -selection clipboard"))
    }
    cat("✅", lang, "version copied to clipboard!\n")
  }, error = function(e) {
    cat("❌ Clipboard copy failed for", lang, "- use saved file instead\n")
  })
}
```

## Export Results Summary

```{r export-summary}

# Create a comprehensive summary of all results
results_summary <- tibble(
  category = c(
    "National Rankings Male", "National Rankings Male", "National Rankings Male",
    "National Rankings Female", "National Rankings Female", "National Rankings Female",
    "Leaders Analysis", "Leaders Analysis", 
    "Biggest Changes", "Biggest Changes", "Biggest Changes", "Biggest Changes",
    "Population Analysis", "Population Analysis",
    "Name Length", "Name Length", "Name Length"
  ),
  metric = c(
    "1st Place", "2nd Place", "3rd Place",
    "1st Place", "2nd Place", "3rd Place", 
    "Male Leader Years as #1", "Female Leader Years as #1",
    "Male Biggest Climber (+places)", "Female Biggest Climber (+places)",
    "Male Biggest Faller (-places)", "Female Biggest Faller (-places)",
    "Most Common Male (total)", "Most Common Female (total)",
    "Average Overall", "Average Male", "Average Female"
  ),
  value = c(
    national_male_1, national_male_2, national_male_3,
    national_female_1, national_female_2, national_female_3,
    paste(male_leader_name, "-", male_leader_years, "years"),
    paste(female_leader_name, "-", female_leader_years, "years"),
    paste(male_biggest_climber, "+", male_climber_gain),
    paste(female_biggest_climber, "+", female_climber_gain),
    paste(male_biggest_faller, "-", male_faller_loss),
    paste(female_biggest_faller, "-", female_faller_loss),
    paste(most_common_male, "-", format(most_common_male_count, big.mark = ",")),
    paste(most_common_female, "-", format(most_common_female_count, big.mark = ",")),
    paste(avg_length_overall, "characters"),
    paste(avg_length_male, "characters"), 
    paste(avg_length_female, "characters")
  )
)

print("Results Summary for Text Generation:")
print(results_summary)

# Save results for potential export
write_csv(results_summary, file.path(output_dir, paste0("name_analysis_summary_", data_year, ".csv")))
cat("\n✅ Results summary exported to CSV\n")
```
